Detecting Facial Expressions in Professional Tennis Matches

### 2017-08-08 Report06-12.Rmd
figure locations
Accessories crosstable

```{r timeDensity, fig.cap="This density plot diplays the lengths of time each API took to detect faces in each image. Most of the images take less than one second to process. There is an outlier for Skybiometry that took almost 5 seconds to process. \\label{fig:timeDensity}"}
times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual") %>% arrange(-time.user.self)
ggplot(times, na.rm=T) + 
  scale_color_manual(values = type.colours) +
  geom_density(aes(x=time.user.self, colour=type)) +
  xlab("Time Taken")
```

>>>>

```{r timeTable, results='asis', fig.cap="\\label{tab:timeTable}"}

times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual") %>% droplevels()

times %>% 
  split(.$type) %>%  map_df(~ summary(.$time.user.self, digits=max(2, getOption("digits")-2))) %>%
  rownames_to_column %>%  gather(var, value, -rowname) %>% 
  spread(rowname, value) %>% select(c("API" = `var`,
                            "Min" = `1`,
                        "1st Qrt" = `2`,
                        "Median"  = `3`,
                        "3rd Qrt" = `5`,
                        "Max"     = `6`)) -> usertime
times %>% 
  split(.$type) %>%  map_df(~ summary(.$time.sys.self, digits=max(2, getOption("digits")-2))) %>%
  rownames_to_column %>%  gather(var, value, -rowname) %>% 
  spread(rowname, value) %>% select(c("API" = `var`,
                            "Min" = `1`,
                        "1st Qrt" = `2`,
                        "Median"  = `3`,
                        "3rd Qrt" = `5`,
                        "Max"     = `6`)) -> systime

cbind(usertime, systime) -> timetable

knitr::kable(timetable, booktabs = TRUE, longtable=TRUE, caption="This table allows comparisons to be made between the  amount of time taken for each API took to detect faces in each image. Most of the images take less than one second to process. Google had the highest maximum time of 4.936", format = "latex")
```
